manuscript_figures

### 2024-07-10 scripts/manuscript_figures.Rmd
calcualting kelp HPI

# Create box plot x axis as type (control and treatment) and y is HPI for kelp 
```{r}

>>>>

# Create box plot x axis as type (control and treatment) and y is HPI for kelp 
```{r}
# First, need to designate control and kelp treatments in the data frame for each year at each site, first filter 2016-2018 years because no 5 and 6 transects where used
# Filter out 2016-2018 YEAR data
HPI.kelp <- subset(morph.filt, YEAR < 2016 | YEAR > 2018)

# Rename KB q to transect 6
HPI.kelp$TRANSECT[HPI.kelp$TRANSECT == "KB q"] <- "6"

# Now create a treatment column that assigns TRANSECTs 5 and 6 from each year as TREATMENT = control and all other transectes TREATMENT = kelp
HPI.kelp <- HPI.kelp %>%
  mutate(TREATMENT = ifelse(TRANSECT %in% c(5, 6), "control", "kelp"))

# Calculate habitat productivity index for all transects
